quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-20 paper-quollr.Rmd
Removed hexgrid from figure 1

## 2-d vis model
hex_grid_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = scurve_umap_scaled, 
             aes(x = emb1, y = emb2), 
             alpha = 0.2, size = 0.5, color = clr_choice) +
  geom_segment(data = tr_from_to_df_scurve,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#33a02c")

>>>>

## 2-d vis model
hex_grid_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_point(data = scurve_umap_scaled, 
             aes(x = emb1, y = emb2), 
             alpha = 0.2, size = 0.5, color = clr_choice) +
  geom_segment(data = tr_from_to_df_scurve,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#33a02c")
